---
title: "rxivistr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rxivistr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Rxivist indexes articles from bioRxiv, a free preprint server by Cold Spring Harbor Laboratory. This package is a client for the Rxivist API and can be used to access metadata from:

  * Metadata on articles published on biorxiv, indexed in the Rxivist
  * Information about authors of the aforementioned articles
  * Usage statistics (e.g. number of downloads for specific paper)

## Installation 

To install rxivistr package, run:

```
devtools::install_github("ikodvanj/rxivstr")
```

## Using rxivstr

Load the package using `library()` function.

```{r}
library(rxivistr)
```

Package contains following functions:

  * `rxivist_search` - retrieves articles with the matching description
  * `article_details` - retrieves data about a single paper and all of its authors
  * `article_downloads` - retrieves monthly download statistics for articles.
  * `authors_rank` - retrieves top 200 authors in the specified category.
  * `author` - provides information about the specified author.
  * `category_list` - retrieves a list of all categories
  * `rxivist_stats` - retrieves basic statistics about the number of articles indexed by the Rxivist.

In the following text, examples are provided for each function.

### rxivist_search

Following function retrieves articles top 5 most downloaded articles related to COVID-19:

```{r}
res <- rxivist_search(search_phrase = "COVID-19", from = "alltime", sortby = "downloads", limit = 5)
dplyr::glimpse(res)
```

### article_details

At the time of writing this vignette, the most downloaded article had an id 72514. With the following function we will retrieve information about this article:

```{r}
res <- article_details(72514)
dplyr::glimpse(res)
```

### article_downloads

To investigate the number of downloads, `article_downloads` function can be used:

```{r}
article_downloads(72514)
```


### authors_rank

To retrieve top 200 authors based on the number of article downloads, authors_rank can be used:

```{r}
res <- authors_rank()
dplyr::glimpse(res)
```


### author

With function author, we can retrieve more information about specific author. 

```{r}
author(295517)
```


### category_list

This function returns a list of all categories to which articles are classified:

```{r}
category_list()
```


### rxivist_stats

Returns information about the number of articles indexed by the Rxivist.

```{r}
res <- rxivist_stats()
dplyr::glimpse(res)
```






